Deep Learning for Automatic Speech Recognition

### 2015-04-28 Paper/Paper.tex
Bibliography update
test before citation

\paragraph{} Despite how well GMMs work, deep learning approaches have overtaken them as the acoustic model for ASR applications for a few reasons. One is simply due to an increase in processing power and more refined algorithms for training and pre-training. But arguably the main reason why deep learning performance outstrips that of GMMs is due to the overall size of the models. For example, in \TODO{cite}, they use a CNN with around 60 million parameters and 650,000 neurons for image classification on the ImageNet dataset. For speech recognition, artificial neural networks are able to take in multiple frames of the acoustic context as input, while GMMs typically look at a single frame and build an expert around it. ANNs normally take in around 9-11 frames, and process the center frame around that window. This extra context allows them to take into account a variety of additional features when modeling the posterior probabilities.

>>>>

\paragraph{} Despite how well GMMs work, deep learning approaches have overtaken them as the acoustic model for ASR applications for a few reasons. One is simply due to an increase in processing power and more refined algorithms for training and pre-training. But arguably the main reason why deep learning performance outstrips that of GMMs is due to the overall size of the models. For example, in \cite{krizhevsky2012imagenet}, they use a CNN with around 60 million parameters and 650,000 neurons for image classification on the ImageNet dataset. For speech recognition, artificial neural networks are able to take in multiple frames of the acoustic context as input, while GMMs typically look at a single frame and build an expert around it. ANNs normally take in around 9-11 frames, and process the center frame around that window. This extra context allows them to take into account a variety of additional features when modeling the posterior probabilities.
